6.829 Final Project: A comparison of bit rate selection algorithms

### 2013-05-17 paper/paper.tex
Minor stuff.

\begin{abstract}
We compare the performance SampleRate and Minstrel, two popular
bit rate selection algorithms that have widespread real-world usage.
We use a trace-based approach to avoid kernel programming and consider
Python implementations of both SampleRate and Minstrel.  We test both
algorithms in multiple real-world scenarios, including scenarios with
mobile clients and noisy environments, to highlight differences
between the two algorithms.  We also introduce improvements to the
Minstrel algorithm that allow for significant gains in throughput.
\end{abstract}

@@

Minstrel and SampleRate perform similarly.  The results suggest that
SampleRate tends to perform slightly better, except in very lossy
links such as the client being far awat from the AP or actively
moving.  Minproved, our improved version of Minstrel, solidly
outperforms both Minstrel and SampleRate.

It seems that the replacement of SampleRate in the Linux kernel may
have been a hasty, since it seems to perform similarly to Minstrel and
it is a much simpler algorithm and thus simpler to adapt to changing
wireless standards.  We are not sure if adjustments to SampleRate can
bring its performance to match that of Minproved, however.

@@

We would like to thank Jonathan Perry and Hari Balakrishnan for their
valuable guidance, as well as Derek Smithies for answering our
questions about Minstrel.

>>>>

\begin{abstract}
We compare the performance SampleRate and Minstrel, two popular bit
rate selection algorithms that have widespread real-world usage.  We
use a trace-based approach to avoid kernel programming and improve
reproducibility and allow analysis.  We test both algorithms in
multiple real-world scenarios, including scenarios with mobile clients
and noisy environments, to highlight differences between the two.  We
also introduce improvements to the Minstrel algorithm that allow for
significant gains in throughput.
\end{abstract}

@@

Minstrel and SampleRate perform similarly.  The results suggest that
SampleRate tends to perform better, except in very lossy
links such as the client being far away from the AP or actively
moving.  Minproved, our improved version of Minstrel, solidly
outperforms both Minstrel and SampleRate.

It seems that the replacement of SampleRate in the Linux kernel may
have been hasty, since it performs similarly to Minstrel in many
situations and in most situations and is a much simpler algorithm, and
thus easier to adapt to changing wireless standards.  We are not sure
if adjustments to SampleRate can bring its performance to match that
of Minproved, however.

@@

We would like to thank Jonathan~Perry and Hari~Balakrishnan for their
valuable guidance, as well as Derek~Smithies for answering our
questions about Minstrel.
